Bootstrapping Domain Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-08 paper.tex
circuit figure

\subsection{Boolean circuits}
As a toy domain, we consider the problem of learning
to build the Boolean circuits out of logic gates.
Now, if we equipped our agent with a full repertoire of
circuit primitives -- XOR gates, multiplexers, etc. -- this problem would be easy,
and we could use sophisticated symbolic search algorithms like SMT solvers to synthesize circuits.
Instead, we gave \system only a NAND gate,
and tasked it with building a set of 250 random circuits made out of
AND, NOT, and OR gates,
as well as 2 or 4 input multiplexers.
\system observes the input/output truth table of the circuits.
This experimental setup is an extension of one introduced in the EC algorithm~\cite{Dechter:2013:BLV:2540128.2540316}.
%% For this domain our recognition model is a simple multilayer perceptron 
%% whose inputs are the input/output examples.
\system learns to build these
circuits by inventing new subroutines that correspond to
logic gates and multiplexers (Figure~\ref{circuitTables}, top).
We compare  with four baselines on 250 held-out circuits:
No NN, which lesions $q$;
RF/DC,
which holds the generative model $(\mathcal{D},\theta)$ fixed and learns
a $q$ only from samples from the fixed generative model --
this is how RobustFill and DeepCoder are trained;
PCFG, which lesions $q$, fixes $\mathcal{D}$, and learns only $\theta$ (so it is analogous to learning the parameters of a PCFG);
and Enum, which does no learning and just enumerates a large frontier.
\begin{figure}
\begin{tabular}{lllll}
  \toprule \system&No NN  & RF/DC & PCFG & Enum\\\midrule
  84\% solved&76\%& 63\%&62\%&62\%\\
  $0.9$ sec&  1.1&1.2&1.3&1.3
  \\\bottomrule
\end{tabular}
\caption{Top: \% held-out Boolean circuits solved by \system and baselines w/ 5sec timeout. Bottom: average search time.}
\end{figure}

\begin{figure}
  \begin{circuitikz} \draw
(0,2) node[and port] (myand1) {}
(0,0) node[and port] (myand2) {}
(2,1) node[xnor port] (myxnor) {}
(myand1.out) -- (myxnor.in 1)
(myand2.out) -- (myxnor.in 2);
\end{circuitikz}
  \end{figure}

>>>>

\subsection{Boolean circuits}
As a toy domain, we consider the problem of learning
to build the Boolean circuits out of logic gates.
Now, if we equipped our agent with a full repertoire of
circuit primitives -- XOR gates, multiplexers, etc. -- this problem would be easy,
and we could use sophisticated symbolic search algorithms like SMT solvers to synthesize circuits.
Instead, we gave \system only a NAND gate,
and tasked it with building a set of 250 random circuits made out of
AND, NOT, and OR gates,
as well as 2 or 4 input multiplexers.
\system observes the input/output truth table of the circuits.
This experimental setup is an extension of one introduced in the EC algorithm~\cite{Dechter:2013:BLV:2540128.2540316}.
%% For this domain our recognition model is a simple multilayer perceptron 
%% whose inputs are the input/output examples.
\system learns to build these
circuits by inventing new subroutines that correspond to
logic gates and multiplexers (Figure~\ref{multiplexer}, top).
We compare  with four baselines on 250 held-out circuits:
No NN, which lesions $q$;
RF/DC,
which holds the generative model $(\mathcal{D},\theta)$ fixed and learns
a $q$ only from samples from the fixed generative model --
this is how RobustFill and DeepCoder are trained;
PCFG, which lesions $q$, fixes $\mathcal{D}$, and learns only $\theta$ (so it is analogous to learning the parameters of a PCFG);
and Enum, which does no learning and just enumerates a large frontier.
\begin{figure}
\begin{tabular}{lllll}
  \toprule \system&No NN  & RF/DC & PCFG & Enum\\\midrule
  84\% solved&76\%& 63\%&62\%&62\%\\
  $0.9$ sec&  1.1&1.2&1.3&1.3
  \\\bottomrule
\end{tabular}
\caption{Top: \% held-out Boolean circuits solved by \system and baselines w/ 5sec timeout. Bottom: average search time.}
\end{figure}

\begin{figure}\centering
  \begin{circuitikz} \draw
    (0,0) node[port] (x) {$x$}
    (x)++(0,-0.3) node[port] (y) {$y$}
    (y)++(0,-0.5) node[port] (z) {$z$}

    (x)++(1.7,-0.15) node[nand port, scale = 0.5] (xy) {}
    (xy) ++ (0,-1) node[nand port, scale = 0.5] (xz) {}
    (xz) ++ (1,0.2) node[nand port, scale = 0.5] (zxz) {}
    (zxz) ++ (1,0.2) node[nand port, scale = 0.5] (m) {}
    (x.out) -- (xy.in 1)
    (y.out) -- (xy.in 2)

    (x.out) -- (xz.in 1)
    (z.out) -- (xz.in 2)

    (xz.out) -- (zxz.in 2)
    (z.out) |- (zxz.in 1)

    (zxz.out) -- (m.in 2)
    (xy.out) |- (m.in 1)

    (m)++(1.2,0) node [port] (l) {\textsc{MUX}$(x,y,z)$}
    ;
%% (0,0) node[and port] (myand2) {}
%% (2,1) node[xnor port] (myxnor) {}
%% (myand1.out) -- (myxnor.in 1)
%% (myand2.out) -- (myxnor.in 2);
  \end{circuitikz}
\caption{\system discovers the above multiplexer circuit, which it uses to make more complicated circuits like the one below.}\label{multiplexer}
  \end{figure}
